
\addcontentsline{toc}{chapter}{Литература} 

\begin{thebibliography}{3}

\bibitem{bib1}
Hillary Clinton's Emails,
\url{https://www.kaggle.com/kaggle/hillary-clinton-emails}.

\bibitem{clinton_research_bib}
Partisanship, Propaganda, and Disinformation: Online Media and the 2016 U.S. Presidential Election // Berkman Klein Center — December 7, 2017.

\bibitem{clinton_oldford_bib}
Analyzing the meta data of Hillary Clinton’s emails.
\url{https://uwaterloo.ca/statistics-and-actuarial-science/news/analyzing-meta-data-hillary-clintons-emails}.

\bibitem{bib_5}
Ron Bekkerman et al., "Automatic Categorization of Email into Folders:
Benchmark Experiments on Enron and SRI Corpora, Technical Report,
University of Massachusetts. 
\url{https://scholarworks.umass.edu/cgi/viewcontent.cgi?article=1217&context=cs_faculty_pubs}.

\bibitem{bib_6}
Jitesh Shetty and Jafar Adibi, "The Enron Email Dataset: Database Schema and Brief Statistical Report," Technical Report, Information Sciences Institute, 2004. \url{http://www.isi.edu/~adibi/Enron/Enron_Dataset_Report.pdf}.

\bibitem{bib_7}
Jitesh Shetty, Jafar Adibi, 2005. Discovering Important Nodes
through Graph Entropy the Case of Enron Email Database,
KDD’2005, Chicago, Illinois.

\bibitem{bib_8}
Ria Kulshrestha. A Beginner’s Guide to Latent Dirichlet Allocation (LDA). \url{https://towardsdatascience.com/latent-dirichlet-allocation-lda-9d1cd064ffa2}

\bibitem{bib5}
Mikolov T., Chen K., Corrado G., Dean J. Efficient Estimation of Word Representations in Vector Space // In Proceedings of Workshop at ICLR. — 2013a.

\bibitem{bib_9}
Victor Roman. Unsupervised Machine Learning: Clustering Analysis. \url{https://towardsdatascience.com/unsupervised-machine-learning-clustering-analysis-d40f2b34ae7e}.

\bibitem{bib234234}
BERTopic. \url{https://maartengr.github.io/BERTopic/}.

\bibitem{bib_1}
Jacob Devlin, Ming-Wei Chang, Kenton Lee, Kristina Toutanova. BERT: Pre-training of Deep Bidirectional Transformers for Language Understanding. 
\url{https://arxiv.org/abs/1810.04805}.

\bibitem{bib_2}
Lena Voita. 
(Introduction to) Transfer Learning. \url{https://lena-voita.github.io/nlp_course/transfer_learning.html}.

\bibitem{bib_3}
Brendan Bailey. Lightning Talk: Clustering with HDBScan. \url{https://towardsdatascience.com/lightning-talk-clustering-with-hdbscan-d47b83d1b03a}.

\bibitem{bib_4}
BERTopic, Topic Visualization. \url{https://maartengr.github.io/BERTopic/tutorial/visualization/visualization.html}.

\bibitem{nltkk}
Natural Language Toolkit.
\url{https://www.nltk.org}.

\bibitem{bib3}
Библиотека spaCy. \url{https://spacy.io/}.

\bibitem{bib8}
Email — An email and MIME handling package. \url{https://docs.python.org/3/library/email.html}.


\bibitem{bib6}
GloVe: Global Vectors for Word Representation. \url{https://nlp.stanford.edu/projects/glove/}.

\bibitem{bib7}
van der Maaten L.J.P., Hinton G.E. Visualizing Data Using t-SNE // Journal of Machine Learning Research. — 2008. — Ноябрь (т. 9).



\end{thebibliography}


